### 2025-04-15 reports/paper/resources/intervention-density-witnin-combos-b.tex
cannot figure out figure

% Created by tikzDevice version 0.12.3.1 on 2023-06-28 16:10:08
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{amssymb}
\usepackage{upgreek}
\usepackage[no-math]{fontspec}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (252.94,180.68);
\end{scope}
\begin{scope}
\path[clip] ( 38.22, 31.50) rectangle (246.94,165.67);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 38.22, 31.50) rectangle (246.94,165.68);
\definecolor{fillColor}{RGB}{211,211,211}

\path[fill=fillColor] ( 47.71, 37.60) rectangle ( 55.01,159.58);

\path[fill=fillColor] ( 55.01, 37.60) rectangle ( 62.31, 37.60);

@@

\path[fill=fillColor] ( 69.61, 37.60) rectangle ( 76.90, 37.60);

\path[fill=fillColor] ( 76.90, 37.60) rectangle ( 84.20, 37.60);

@@

\path[fill=fillColor] (106.10, 37.60) rectangle (113.39, 37.60);

\path[fill=fillColor] (113.39, 37.60) rectangle (120.69, 37.60);

@@

\path[draw=drawColor,line width= 0.4pt] ( 47.71, 37.60) rectangle ( 55.01, 68.10);

\path[draw=drawColor,line width= 0.4pt] ( 55.01, 37.60) rectangle ( 62.31, 37.60);

@@

\path[draw=drawColor,line width= 0.4pt] ( 69.61, 37.60) rectangle ( 76.90, 37.60);

\path[draw=drawColor,line width= 0.4pt] ( 76.90, 37.60) rectangle ( 84.20, 37.60);

@@

\path[draw=drawColor,line width= 0.4pt] (106.10, 37.60) rectangle (113.39, 37.60);

\path[draw=drawColor,line width= 0.4pt] (113.39, 37.60) rectangle (120.69, 37.60);

\path[draw=drawColor,line width= 0.4pt] (120.69, 37.60) rectangle (127.99, 98.59);

@@

\path[draw=drawColor,line width= 0.4pt] (135.29, 37.60) rectangle (142.58, 68.10);

\path[draw=drawColor,line width= 0.4pt] (142.58, 37.60) rectangle (149.88, 37.60);

\path[draw=drawColor,line width= 0.4pt] (149.88, 37.60) rectangle (157.18, 37.60);

@@

\path[draw=drawColor,line width= 0.4pt] (171.78, 37.60) rectangle (179.07, 37.60);

\path[draw=drawColor,line width= 0.4pt] (179.07, 37.60) rectangle (186.37, 37.60);

@@

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 7pt off 3pt ,line join=round] (120.69, 31.50) -- (120.69,165.67);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 38.22, 31.50) rectangle (246.94,165.68);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 33.27, 34.85) {0};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 33.27, 65.34) {10};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 33.27, 95.83) {20};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 33.27,126.33) {30};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 33.27,156.82) {40};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.4pt,line join=round] ( 35.47, 37.60) --
	( 38.22, 37.60);

\path[draw=drawColor,line width= 0.4pt,line join=round] ( 35.47, 68.10) --
	( 38.22, 68.10);

\path[draw=drawColor,line width= 0.4pt,line join=round] ( 35.47, 98.59) --
	( 38.22, 98.59);

\path[draw=drawColor,line width= 0.4pt,line join=round] ( 35.47,129.08) --
	( 38.22,129.08);

\path[draw=drawColor,line width= 0.4pt,line join=round] ( 35.47,159.58) --
	( 38.22,159.58);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.4pt,line join=round] ( 47.71, 28.75) --
	( 47.71, 31.50);

\path[draw=drawColor,line width= 0.4pt,line join=round] (106.10, 28.75) --
	(106.10, 31.50);

\path[draw=drawColor,line width= 0.4pt,line join=round] (164.48, 28.75) --
	(164.48, 31.50);

\path[draw=drawColor,line width= 0.4pt,line join=round] (222.86, 28.75) --
	(222.86, 31.50);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{drawColor}{RGB}{0,0,0}

@@

\path[fill=fillColor] (168.95,143.84) rectangle (244.95,163.87);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (168.95,157.35) {Target exposure limit:};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (168.95,146.34) rectangle (176.95,154.34);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 7pt off 3pt ,line join=round] (172.95,146.34) -- (172.95,154.34);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (178.95,147.59) {0.25 mg/m$^3$};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (168.95,113.81) rectangle (240.85,141.84);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (168.95,135.32) {Distribution:};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (168.95,124.31) rectangle (176.95,132.31);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{fillColor}{RGB}{211,211,211}

\path[fill=fillColor] (168.95,124.31) rectangle (176.95,132.31);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (168.95,116.31) rectangle (176.95,124.31);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt] (169.45,116.81) rectangle (176.45,123.81);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (178.95,125.55) {Post-intervention};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (178.95,117.55) {Observed};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (  2.36,170.34) {b)};
\end{scope}
\end{tikzpicture}

>>>>

% Created by tikzDevice version 0.12.3.1 on 2025-04-15 00:28:46
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{amssymb}
\usepackage{upgreek}
\usepackage[no-math]{fontspec}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (252.94,180.68);
\end{scope}
\begin{scope}
\path[clip] ( 38.23, 31.51) rectangle (246.94,165.67);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 38.23, 31.51) rectangle (246.94,165.67);
\definecolor{fillColor}{RGB}{211,211,211}

\path[fill=fillColor] ( 47.71, 37.60) rectangle ( 55.01, 37.60);

\path[fill=fillColor] ( 55.01, 37.60) rectangle ( 62.31,159.58);

@@

\path[fill=fillColor] ( 69.61, 37.60) rectangle ( 76.91, 37.60);

\path[fill=fillColor] ( 76.91, 37.60) rectangle ( 84.20, 37.60);

@@

\path[fill=fillColor] (106.10, 37.60) rectangle (113.40, 37.60);

\path[fill=fillColor] (113.40, 37.60) rectangle (120.69, 37.60);

@@

\path[draw=drawColor,line width= 0.4pt] ( 47.71, 37.60) rectangle ( 55.01, 37.60);

\path[draw=drawColor,line width= 0.4pt] ( 55.01, 37.60) rectangle ( 62.31, 98.59);

@@

\path[draw=drawColor,line width= 0.4pt] ( 69.61, 37.60) rectangle ( 76.91, 37.60);

\path[draw=drawColor,line width= 0.4pt] ( 76.91, 37.60) rectangle ( 84.20, 37.60);

@@

\path[draw=drawColor,line width= 0.4pt] (106.10, 37.60) rectangle (113.40, 37.60);

\path[draw=drawColor,line width= 0.4pt] (113.40, 37.60) rectangle (120.69, 37.60);

\path[draw=drawColor,line width= 0.4pt] (120.69, 37.60) rectangle (127.99, 37.60);

@@

\path[draw=drawColor,line width= 0.4pt] (135.29, 37.60) rectangle (142.59, 37.60);

\path[draw=drawColor,line width= 0.4pt] (142.59, 37.60) rectangle (149.88, 37.60);

\path[draw=drawColor,line width= 0.4pt] (149.88, 37.60) rectangle (157.18, 98.59);

@@

\path[draw=drawColor,line width= 0.4pt] (171.78, 37.60) rectangle (179.08, 37.60);

\path[draw=drawColor,line width= 0.4pt] (179.08, 37.60) rectangle (186.37, 37.60);

@@

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 7pt off 3pt ,line join=round] (120.69, 31.51) -- (120.69,165.67);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 38.23, 31.51) rectangle (246.94,165.67);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 33.28, 34.85) {0};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 33.28, 65.34) {10};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 33.28, 95.83) {20};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 33.28,126.33) {30};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 33.28,156.82) {40};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.4pt,line join=round] ( 35.48, 37.60) --
	( 38.23, 37.60);

\path[draw=drawColor,line width= 0.4pt,line join=round] ( 35.48, 68.10) --
	( 38.23, 68.10);

\path[draw=drawColor,line width= 0.4pt,line join=round] ( 35.48, 98.59) --
	( 38.23, 98.59);

\path[draw=drawColor,line width= 0.4pt,line join=round] ( 35.48,129.08) --
	( 38.23,129.08);

\path[draw=drawColor,line width= 0.4pt,line join=round] ( 35.48,159.58) --
	( 38.23,159.58);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.4pt,line join=round] ( 47.71, 28.76) --
	( 47.71, 31.51);

\path[draw=drawColor,line width= 0.4pt,line join=round] (106.10, 28.76) --
	(106.10, 31.51);

\path[draw=drawColor,line width= 0.4pt,line join=round] (164.48, 28.76) --
	(164.48, 31.51);

\path[draw=drawColor,line width= 0.4pt,line join=round] (222.86, 28.76) --
	(222.86, 31.51);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{drawColor}{RGB}{0,0,0}

@@

\path[fill=fillColor] (168.95,144.09) rectangle (244.95,164.62);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (168.95,158.10) {Target exposure limit:};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (168.95,146.59) rectangle (176.95,154.59);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 7pt off 3pt ,line join=round] (172.95,146.59) -- (172.95,154.59);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (178.95,147.84) {0.25 mg/m$^3$};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (168.95,113.06) rectangle (240.85,141.59);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (168.95,135.07) {Distribution:};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (168.95,123.56) rectangle (176.95,131.56);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{fillColor}{RGB}{211,211,211}

\path[fill=fillColor] (168.95,123.56) rectangle (176.95,131.56);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (168.95,115.56) rectangle (176.95,123.56);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt] (169.45,116.06) rectangle (176.45,123.06);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (178.95,124.80) {Post-intervention};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (178.95,116.80) {Observed};
\end{scope}
\end{tikzpicture}
